Fast Neural Machine Translation Implementation

### 2018-05-17 wnmt.2018/wnmt.tex
turn on timings

@@

\usepackage[letterpaper]{geometry}
%\usepackage{amta2016}
\usepackage{url}
\usepackage{natbib}
\usepackage{layout}

@@

\newcommand{\confname}{AMTA 2016}
\newcommand{\website}{\protect\url{http://www.amtaweb.org/}}
\newcommand{\contactname}{research track co-chair Lane Schwartz}
\newcommand{\contactemail}{lanes@illinois.edu} 
\newcommand{\conffilename}{amta2016}
\newcommand{\downloadsite}{\protect\url{http://www.amtaweb.org/}}
\newcommand{\paperlength}{$12$ (twelve)}
\newcommand{\shortpaperlength}{$6$ (six)}

%% do not add any other page- or text-size instruction here

\parskip=0.00in

\begin{document}

% \mtsummitHeader{x}{x}{xxx-xxx}{2016}{45-character paper description goes here}{Author(s) initials and last name go here}
\title{\bf Fast Neural Machine Translation Implementation}

\author{\name{\bf Hieu Hoang} \hfill  \addr{hieu@hoang.co.uk}\\ 
        \addr{}
\AND
       \name{\bf Tomasz Dwojak} \hfill \addr{t.dwojak@amu.edu.pl}\\
        \addr{Adam Mickiewicz University}
\AND
       \name{\bf Rihards Krislauks} \hfill \addr{rihards.krislauks@tilde.lv}\\
        \addr{Tilde}
\AND
       \name{\bf Daniel Torregrosa} \hfill \addr{dtorregrosa@dlsi.ua.es}\\
        \addr{Universitat d’Alacant}
\AND
       \name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
       %\name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
        \addr{University of Edinburgh, Scotland}
}

\maketitle
\pagestyle{empty}

\begin{abstract}

@@

\end{document}
\grid
\grid

>>>>

%
% File acl2018.tex
%
%% Based on the style files for ACL-2017, with some changes, which were, in turn,
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

@@

\usepackage{url}

@@

\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

% \mtsummitHeader{x}{x}{xxx-xxx}{2016}{45-character paper description goes here}{Author(s) initials and last name go here}
\title{Fast Neural Machine Translation Implementation}

\author{Hieu Hoang \\
  University of Edinburgh, Scotland \\
  {\tt hieu@hoang.co.uk} \\
  \And
  Tomasz Dwojak \\
  Adam Mickiewicz University \\
  {\tt t.dwojak@amu.edu.pl} \\
  \And
  Rihards Krislauks \\
  Tilde \\
  {\tt rihards.krislauks@tilde.lv} \\
  \And
  Daniel Torregrosa \\
  Universitat d’Alacant \\
  {\tt dtorregrosa@dlsi.ua.es} \\
  \And
  Kenneth Heafield \\
  University of Edinburgh, Scotland \\
  {\tt kheafiel@inf.ed.ac.uk} \\
  }

\date{}

\begin{document}
\maketitle
\begin{abstract}

@@

\end{document}
